\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-20 paper/main.tex
.

We find that the model using ontology-based features
(\textit{OntoPred}) is showing better performance on STITCH compared
to using only molecular features. We also observe that only the model
using ontology-based features results in increased performance when
incorporating the PPI graph. This increase can be observed with
different graph neural network architectures and configurations. While
the {\em GCNConv} and {\em GENConv} architecture already shows some
minor improvement, the \textit{ResGraphConv} blocks add a large amount
of additional learnable parameters to the network, leading to more
expressive power. To test whether the improvement is due to the number
of learnable parameters added or the result of better exploiting the
information about PPIs, we experiment with a graph model in which all
graph convolutional neural layers in the residual blocks are removed,
resulting in a non--graph model. This pruned network, with no
information on the protein--protein interactions, reached very similar
results to the original \textit{OntoPred} model and showed no
improvement.

Furthermore, these major improvements are only provided by the \textit{GENConv} graph convolution scheme as part of the ResGraphConv blocks, as \textit{GCNConv} and other related graph convolutional methods fail to achieve any gain in comparison to the plain \textit{OntoPred} performance even when combined with the residual blocks. The discrepancy of {\em GENConv} and other graph convolutional methods may be founded in numerical stability and fading signals, as described in the introduction of the {\em GENConv} method.

As the inclusion of graph information increases performance, we conclude that information about protein
functions localizes on the graph while molecular features do not.

>>>>

We find that the model using ontology-based features
(\textit{OntoPred}) is showing better performance on STITCH compared
to using only molecular features. We also observe that only the model
using ontology-based features results in increased performance when
incorporating the PPI graph. This increase can be observed with
different graph neural network architectures and configurations. While
the {\em GCNConv} and {\em GENConv} architecture already shows some
minor improvement, the \textit{ResGraphConv} blocks add a large amount
of additional learnable parameters to the network, leading to more
expressive power. To test whether the improvement is due to the number
of learnable parameters added or the result of better exploiting the
information about PPIs, we experiment with a graph model in which all
graph convolutional neural layers in the residual blocks are removed,
resulting in a model with similar parameters but without the ability
to use graph-based information. This pruned network, with no
information on the protein--protein interactions, reached very similar
results to the original \textit{OntoPred} model and showed no
improvement.

The improvements when including the graph are only provided by the
\textit{GENConv} graph convolution scheme which includes the
ResGraphConv blocks; \textit{GCNConv} and other graph
convolutional methods fail to achieve any gain in comparison to the
plain \textit{OntoPred} performance even when combined with the
residual blocks. The discrepancy between {\em GENConv} and other graph
convolutional methods may be the result of numerical instability and
fading signals \cite{}.
Nevertheless, our results demonstrate that the inclusion of graph
information increases performance when ontology-based features are
used, which allows us to conclude that information about protein
functions localizes on the graph whereas molecular features do not.
